|

### 2020-10-11 paper/article.Rmd
edits to first three sections

Subjects who received monetary incentives, either alone or in pairs, visited
fewer houses than those who did not earn financial rewards. While the result
may seem counter-intuitive, it actually attests the effectiveness of the
treatment. This is because we offered incentives for subjects to exterminate
larvae and find breeding sites, but not to visit a greater number of
households. As a result, participants in the two treatment groups did a
thorough job in each household, which explains the lower number of visits
during the allotted time. We find that subjects in the individual and in the
collective bonus groups visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$)
and $-7.554$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) households, respectively.

Our second indicator provides further evidence in favour of our argument. We
see that the two groups which earned performance bonuses spent more time in the
households, as their number of houses visited for less than two minutes is
significantly lower than those of the control condition. On average,
participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
XXX], $p-$value $= 0.XXX$) fewer houses than the control, and those in the
collective bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).

Incentivised teams find and clean more breeding sites than non-incentivised
ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX],
$p-$value $= 0.XXX$) more breeding sites than the non-incentivised control
group. The effect for those in the collective bonus group is 21.512 (CI: [XXX,
XXX], $p-$value $= 0.XXX$), slightly smaller than for the first treatment.

Collective incentivized teams are more effective in finding larvae. In our
study, collectively incentivized subjects have 16.3\% more chance to find
larvae than non incentivized workers. Finding larvae is harder, and the
detection chances profit from teamwork. If teams are cooperating, searching the
house becomes more natural, and they can coordinate to do a more thorough job.
Additionally, the detection tends to be excludable: one individual finding
larvae makes the chances of keep finding larvae in the household considerably
smaller. Collective bonus is not excludable within the teams, making them
cooperate more to get the reward.

>>>>

Subjects who received monetary incentives, either alone or in pairs, visited
fewer houses than those who did not earn financial rewards. While the result
seems counter-intuitive, it actually attests the effectiveness of the
treatment. This is because we offered incentives for subjects to exterminate
larvae and find breeding sites, not to visit a greater number of households. As
a result, participants in the two treatment groups did a thorough job in each
household, which explains the lower number of visits during the allotted time.
We find that subjects in the individual and in the collective bonus groups
visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) and $-7.554$ (CI: [XXX,
XXX], $p-$value $= 0.XXX$) households, respectively.

Our second indicator provides further evidence in favour of our argument. We
see that the two groups which earned performance bonuses spent more time in the
households, as their number of houses visited for less than two minutes is
significantly lower than those of the control condition. On average,
participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
XXX], $p-$value $= 0.XXX$) houses than the control, and those in the collective
bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).

Incentivised teams find and clean more breeding sites than non-incentivised
ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX],
$p-$value $= 0.XXX$) more breeding sites than the non-incentivised control
group. The effect for those in the collective bonus group is 21.512 (CI: [XXX,
XXX], $p-$value $= 0.XXX$), slightly smaller than for the individual treatment.

Teams which received collective bonuses are the most effective in finding
larvae. Subjects who worked in pairs have a 16.3% (CI: [XXX, XXX], $p-$value =
$0.XXX$) higher likelihood of finding larvae than those in the control group.
Locating mosquito larvae is a difficult task, thus the probability of
successfully completing the task increases when subjects work in teams.
Furthermore, our collective bonus scheme was not excludable within the teams,
thus health care workers had an incentive to cooperate and receive higher
rewards.

## Disease Incidence
\label{sub:incidence}

We evaluate the effect of the treatment on the disease incidence with two
models. The first is a differences-in-differences model that assesses whether
the intervention _per se_ had any effect on dengue hospitalisations in the city
of Rio Verde. The second model compares disease incidence in each of the
treatment statuses with disease incidence in the control group. The unit of
analysis is the census tract. Table \ref{tab:incidence} displays the results
for our first model, in which we test the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

\begin{table}[!htbp] \centering 
  \caption{Disease Incidence -- Differences in Differences Model} 
  \label{difindifdiseases} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (Indv. x Collect.) \\ 
\hline \\[-1.8ex] 
 DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:} & \multicolumn{5}{r}{DID stands for the differences-in-differences estimator.}
& \multicolumn{5}{r}{Robust standard errors clustered at the census tract level in parenthesis.} \\ 
& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
= $0.XXX$) if we take both treatments and compare them with the control group.
The result is consistent around fewer weeks before and after the intervention,
but it does not reach conventional levels of statistical significance. This
suggests that the treatment effect is probably small. The comparison between
the two treatment statuses show an impact of 2.9\% fewer infections in the
collective bonus group. However, the result is also not statistically
significant.

In our second model, we measure the effect of the reward schemes on the number
of hospitalisations per census tract. Table \ref{fig:census} shows
hospitalisation counts before the intervention, and then 15, 30, 60, 90, and
between 15 to 30 days after the treatment.

\begin{table}[!htbp]
  \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
  \label{regdiseaseinc1} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Before & 15 Days & 30 Days & 60 Days & 90 Days & 30-60 Days \\ 
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex] 
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
  & & & & & & \\ 
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{Robust standard errors clustered at the census tract level in parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular} 
\end{table}

Compared to the control group, neither treatment had an impact on disease
incidence in the Rio Verde census tracts. Yet, the coefficients are negative,
what indicates that should an impact have occurred, the intervention would
have lowered dengue incidence in the treated areas.

# Discussion
\label{sec:discussion}
